results

### 2023-02-13 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
added text
corrected document title

---
output: html_document
bibliography: ER_ED.bib
csl: apa7.csl
editor_options: 
  markdown: 
    wrap: sentence
---

```{r SetupMethod, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)

@@

# 3. Method

>>>>

---
title: "results"
author: "Christoph Scheffel"
output: html_document
---

```{r SetupResults, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)

@@

# 3. Results

## 3.1 Participants and descriptive statistics

Data collection took place between `r acqui_time[1]` and `r acqui_time[2]`.

## 3.2. Confirmatory analyses

## 3.3. Exploratory analyses
